\Large Analyzing the Supreme Court Citation Network

### 2017-12-05 Tex/paper.tex
new inferential results

@@

\begin{table}[H]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -5.319                                                 & -5.392                                                     & -5.243                                                     \\ \hline
Instar(2)               & 0.018                                                   & 0.017                                                      & 0.019                                                      \\ \hline
Outstar(2)              & 0.018                                                  & 0.016                                                      & 0.022                                                      \\ \hline
Mutual                  & 3.179                                                   & 2.694                                                 & 3.565                                                      \\ \hline
Triangle                & 1.531                                                   & 1.493                                                      & 1.563                                                      \\ \hline
MQ Score                & 0.041                                                   & 0.018                                                      & 0.063                                                      \\ \hline
Same Issue Area         & 1.061                                                   & 1.028                                                      & 1.099                                                      \\ \hline
Year Difference         & 0.010                                                   & 0.008                                                     & 0.013                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the time period 1937-2001}
\label{bootMPLE_total}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -5.391                                                 & -5.506                                                     & -5.244                                                     \\ \hline
Instar(2)               & 0.035                                                   & 0.028                                                      & 0.042                                                      \\ \hline
Outstar(2)              & 0.015                                                   & 0.0003                                                      & 0.017                                                      \\ \hline
Mutual                  & 4.785                                                   & 3.616                                                 & 5.749                                                      \\ \hline
Triangle                & 1.377                                                   & 1.271                                                      & 1.513                                                      \\ \hline
MQ Score                & -0.018                                                   & -0.095                                                      & 0.061                                                      \\ \hline
Same Issue Area         & 1.229                                                   & 1.126                                                      & 1.327                                                      \\ \hline
Year Difference         & -0.077                                                   & -0.096                                                     & -0.061                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the time period when Fred M. Vinson was chief justice.}
\label{bootMPLE_vinson}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -5.032                                                 & -5.140                                                     & -4.931                                                     \\ \hline
Instar(2)               & 0.028                                                   & 0.025                                                      & 0.032                                                      \\ \hline
Outstar(2)              & 0.018                                                   & 0.015                                                      & 0.022                                                      \\ \hline
Mutual                  & 3.166                                                   & 1.826                                                 & 4.565                                                      \\ \hline
Triangle                & 1.520                                                   & 1.449                                                      & 1.599                                                      \\ \hline
MQ Score                & -0.101                                                   & -0.149                                                      & -0.052                                                      \\ \hline
Same Issue Area         & 1.349                                                   & 1.289                                                      & 1.408                                                      \\ \hline
Year Difference         & -0.031                                                   & -0.038                                                     & -0.026                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the time period when Earl Warren was chief justice.}
\label{bootMPLE_warren}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -3.952                                                 & -4.017                                                     & -3.882                                                     \\ \hline
Instar(2)               & 0.015                                                   & 0.013                                                      & 0.016                                                      \\ \hline
Outstar(2)              & 0.004                                                   & 0.002                                                      & 0.006                                                      \\ \hline
Mutual                  & 2.558                                                   & 1.425                                                 & 3.719                                                      \\ \hline
Triangle                & 1.383                                                   & 1.333                                                      & 1.440                                                      \\ \hline
MQ Score                & -0.084                                                   & -0.101                                                      & -0.059                                                      \\ \hline
Same Issue Area         & 0.959                                                   & 0.911                                                      & 1.008                                                      \\ \hline
Year Difference         & -0.017                                                   & -0.019                                                     & -0.015                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the time period when Warren E. Burger was chief justice.}
\label{bootMPLE_burger}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -3.614                                                 & -3.701                                                     & -3.525                                                     \\ \hline
Instar(2)               & 0.015                                                   & 0.013                                                      & 0.016                                                      \\ \hline
Outstar(2)              & 0.002                                                   & -0.002                                                      & 0.004                                                      \\ \hline
Mutual                  & 9.635                                                  & 6.426                                                 & 10.834                                                      \\ \hline
Triangle                & 1.551                                                   & 1.489                                                      & 1.620                                                      \\ \hline
MQ Score                & -0.007                                                   & -0.039                                                      & 0.028                                                      \\ \hline
Same Issue Area         & 0.855                                                   & 0.794                                                      & 0.916                                                      \\ \hline
Year Difference         & -0.016                                                   & -0.018                                                     & -0.014                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the time period when William Rehnquist was chief justice.}
\label{bootMPLE_rehnquist}
\end{table}

>>>>

\textbf{Sociality} Citations sent beget citations sent.  For each case discussed, often related cases to discuss, even those that do not cite each other. For each case that applies, there is likely a case that needs to be discussed in terms of why it does not apply. Justices often clarify not only those legal principles that apply, but often those that do not. When multiple lines of legal reasoning are drawn upon to justify a decision, often more are discussed in terms of their lack of applicability.

"1. The "overbreadth" doctrine is not applicable here. There is nothing in the record to indicate that \S 28.04 will have any different impact on any third parties' interests in free speech than it has on appellees' interests, and appellees have failed to identify any significant difference between their claim that \S 28.04 is invalid on overbreadth grounds and their claim that it is unconstitutional when applied to their signs during a political campaign. Thus, it is inappropriate to entertain an overbreadth challenge to \S 28.04. Pp. 466 U. S. 796-803."

https://supreme.justia.com/cases/federal/us/466/789/

''No allegations of racial or class-based invidiously discriminatory animus are required to establish a cause of action under the first part of  1985(2). The statutory provisions now codified at \S 1985 were originally enacted as \S 2 of the Civil Rights Act of 1871, and the substantive meaning of the 1871 Act has not been changed. The provisions relating to institutions and processes of the Federal Government (including the first part of \S 1985(2)) -- unlike those encompassing activity that is usually of primary state concern (including the second part of \S 1985(2) and the part of \P 1985(3) involved in Griffin, supra -- contain no language requiring that the conspirators act with intent to deprive their victims of the equal protection of the laws. Thus, the reasoning of Griffin is not applicable here, and, given the structure of \S 2 of the 1871 Act, it is clear''

https://supreme.justia.com/cases/federal/us/460/719/

@@

\begin{table}[H]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{EFEFEF}}l |l|l|l|l|}
\hline
                                       & \cellcolor[HTML]{EFEFEF}Estimate & \cellcolor[HTML]{EFEFEF}Lower Bound & \cellcolor[HTML]{EFEFEF}Upper Bound & \cellcolor[HTML]{EFEFEF}Significance \\ \hline
Edges                                  & -5.151                           & -5.269                              & -5.038                              & *                                    \\ \hline
Instar(2)                              & 0.00026                          & 0.00023                             & 0.00030                             & *                                    \\ \hline
Outstar(2)                             & 0.00010                          & 0.00004                             & 0.00018                             & *                                    \\ \hline
Mutual                                 & 0.190                            & 0.139                               & 0.260                               & *                                    \\ \hline
Triangle                               & 0.039                            & 0.038                               & 0.041                               & *                                    \\ \hline
Martin Quinn Score                     & -0.0017                          & -0.0021                             & -0.0010                             & *                                    \\ \hline
Same Issue Area Homophily              & 0.027                            & 0.026                               & 0.028                               & *                                    \\ \hline
Year Difference                        & -0.0005                          & -0.0006                             & -0.0004                             & *                                    \\ \hline
$(\text{Year Differnce})^2$            & 7.498e-08                        & 4.629e-08                           & 1.057e-07                           & *                                    \\ \hline
{\small Receiver Abs Diff MQ Score in Majority} & 0.002                            & -0.005                              & 0.009                               &                                      \\ \hline
{\small Receiver Number Justices in Majority}   & -0.012                           & -0.022                              & -0.0002                             & *                                    \\ \hline
Receiver  Sender Year                  & 0.0005                           & 0.0004                              & 0.0006                              & *                                    \\ \hline
Sender Same Issue Area 2               & 0.155                            & 0.091                               & 0.214                               & *                                    \\ \hline
Sender Same Issue Area 3               & -0.095                           & -0.189                              & -0.008                              & *                                    \\ \hline
Sender Same Issue Area 4               & 0.401                            & 0.324                               & 0.481                               & *                                    \\ \hline
Sender Same Issue Area 5               & 0.262                            & 0.089                               & 0.450                               & *                                    \\ \hline
Sender Same Issue Area 6               & 0.350                            & 0.222                               & 0.472                               & *                                    \\ \hline
Sender Same Issue Area 7               & 0.438                            & 0.361                               & 0.520                               & *                                    \\ \hline
Sender Same Issue Area 8               & 0.064                            & 0.002                               & 0.128                               & *                                    \\ \hline
Sender Same Issue Area 9               & 0.181                            & 0.123                               & 0.244                               & *                                    \\ \hline
Sender Same Issue Area 10              & 0.305                            & 0.224                               & 0.380                               & *                                    \\ \hline
Sender Same Issue Area 11              & -0.187                           & -0.371                              & -0.003                              & *                                    \\ \hline
Sender Same Issue Area 12              & -0.244                           & -0.348                              & -0.149                              & *                                    \\ \hline
Sender Same Issue Area 13              & -0.022                           & -0.270                              & 0.202                               &                                      \\ \hline
Sender Same Issue Area 14              & -0.418                           & -0.613                              & -0.269                              & *                                    \\ \hline
Receiver Same Issue Area 2             & 0.204                            & 0.126                               & 0.278                               & *                                    \\ \hline
Receiver Same Issue Area 3             & 0.077                            & -0.030                              & 0.183                               &                                      \\ \hline
Receiver Same Issue Area 4             & 0.459                            & 0.352                               & 0.573                               & *                                    \\ \hline
Receiver Same Issue Area 5             & 0.320                            & 0.094                               & 0.529                               & *                                    \\ \hline
Receiver Same Issue Area 6             & 0.411                            & 0.194                               & 0.615                               & *                                    \\ \hline
Receiver Same Issue Area 7             & 0.391                            & 0.312                               & 0.480                               & *                                    \\ \hline
Receiver Same Issue Area 8             & 0.210                            & 0.146                               & 0.274                               & *                                    \\ \hline
Receiver Same Issue Area 9             & 0.230                            & 0.161                               & 0.315                               & *                                    \\ \hline
Receiver Same Issue Area 10            & 0.495                            & 0.393                               & 0.569                               & *                                    \\ \hline
Receiver Same Issue Area 11            & 0.196                            & -0.033                              & 0.389                               &                                      \\ \hline
Receiver Same Issue Area 12            & 0.177                            & 0.026                               & 0.348                               & *                                    \\ \hline
Receiver Same Issue Area 13            & 0.896                            & 0.555                               & 1.194                               & *                                    \\ \hline
Receiver Same Issue Area 14            & -0.137                           & -0.645                              & 0.233                               &                                      \\ \hline
\end{tabular}
\caption{Bootstrapped MPLE Results for the time period 1937-2001}
\label{bootMPLE_total}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{EFEFEF}}l |l|l|l|l|}
\hline
                                            & \cellcolor[HTML]{EFEFEF}Estimate & \cellcolor[HTML]{EFEFEF}Lower Bound & \cellcolor[HTML]{EFEFEF}Upper Bound & \cellcolor[HTML]{EFEFEF}Significance \\ \hline
Edges                                       & -4.524                           & -4.736                              & -4.331                              & *                                    \\ \hline
Instar(2)                                   & 0.00041                          & 0.00038                             & 0.00045                             & *                                    \\ \hline
Outstar(2)                                  & 0.00012                          & 0.00007                             & 0.00017                             & *                                    \\ \hline
Mutual                                      & 0.060                            & 0.034                               & 0.089                               & *                                    \\ \hline
Triangle                                    & 0.033                            & 0.032                               & 0.035                               & *                                    \\ \hline
Martin Quinn Score                          & -0.0001                          & -0.0007                             & 0.0006                              &                                      \\ \hline
Same Issue Area Homophily                   & 0.025                            & 0.024                               & 0.026                               & *                                    \\ \hline
Year Difference                             & -0.001                           & -0.0012                             & -0.0009                             & *                                    \\ \hline
$(\text{Year Differnce})^2$                 & 4.108e-07                        & 3.413e-07                           & 4.909e-07                           & *                                    \\ \hline
{\small Receiver Abs Diff MQ Score in Majority} & 0.036                            & 0.027                               & 0.047                               & *                                    \\ \hline
{\small Receiver Number Justices in Majority}        & -0.004                           & -0.018                              & 0.011                               &                                      \\ \hline
Receiver  Sender Year                       & -0.040                           & -0.0002                             & 0.0001                              &                                      \\ \hline
Sender Same Issue Area 2                    & 0.172                            & 0.098                               & 0.249                               & *                                    \\ \hline
Sender Same Issue Area 3                    & -0.187                           & -0.301                              & -0.067                              & *                                    \\ \hline
Sender Same Issue Area 4                    & 0.535                            & 0.424                               & 0.625                               & *                                    \\ \hline
Sender Same Issue Area 5                    & 0.662                            & 0.439                               & 0.860                               & *                                    \\ \hline
Sender Same Issue Area 6                    & 0.656                            & 0.468                               & 0.831                               & *                                    \\ \hline
Sender Same Issue Area 7                    & 0.478                            & 0.353                               & 0.598                               & *                                    \\ \hline
Sender Same Issue Area 8                    & 0.255                            & 0.176                               & 0.336                               & *                                    \\ \hline
Sender Same Issue Area 9                    & 0.385                            & 0.301                               & 0.469                               & *                                    \\ \hline
Sender Same Issue Area 10                   & 0.431                            & 0.295                               & 0.548                               & *                                    \\ \hline
Sender Same Issue Area 11                   & 0.165                            & -0.204                              & 0.444                               &                                      \\ \hline
Sender Same Issue Area 12                   & 0.168                            & 0.016                               & 0.302                               & *                                    \\ \hline
Sender Same Issue Area 13                   & 0.694                            & 0.162                               & 1.102                               & *                                    \\ \hline
Sender Same Issue Area 14                   & -0.054                           & -0.525                              & 0.325                               &                                      \\ \hline
Receiver Same Issue Area 2                  & 0.212                            & 0.122                               & 0.311                               & *                                    \\ \hline
Receiver Same Issue Area 3                  & -0.140                           & -0.291                              & 0.017                               &                                      \\ \hline
Receiver Same Issue Area 4                  & 0.538                            & 0.375                               & 0.699                               & *                                    \\ \hline
Receiver Same Issue Area 5                  & 0.426                            & 0.189                               & 0.653                               & *                                    \\ \hline
Receiver Same Issue Area 6                  & 0.512                            & 0.197                               & 0.777                               & *                                    \\ \hline
Receiver Same Issue Area 7                  & 0.510                            & 0.385                               & 0.649                               & *                                    \\ \hline
Receiver Same Issue Area 8                  & 0.372                            & 0.283                               & 0.468                               & *                                    \\ \hline
Receiver Same Issue Area 9                  & 0.243                            & 0.134                               & 0.347                               & *                                    \\ \hline
Receiver Same Issue Area 10                 & 0.555                            & 0.388                               & 0.709                               & *                                    \\ \hline
Receiver Same Issue Area 11                 & -0.318                           & -0.847                              & 0.094                               &                                      \\ \hline
Receiver Same Issue Area 12                 & 0.626                            & 0.478                               & 0.798                               & *                                    \\ \hline
Receiver Same Issue Area 13                 & 1.342                            & 0.561                               & 1.696                               & *                                    \\ \hline
Receiver Same Issue Area 14                 & NA                               & NA                                  & NA                                  &                                      \\ \hline
\end{tabular}
\caption{Bootstrapped MPLE Results for the time period when Warren E. Burger was chief justice.}
\label{bootMPLE_burger}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{EFEFEF}}l |l|l|l|l|}
\hline
                                       & \cellcolor[HTML]{EFEFEF}Estimate & \cellcolor[HTML]{EFEFEF}Lower Bound & \cellcolor[HTML]{EFEFEF}Upper Bound & \cellcolor[HTML]{EFEFEF}Significance \\ \hline
Edges                                  & -4.271                           & -4.735                              & -3.779                              & *                                    \\ \hline
Instar(2)                              & 0.00034                          & 0.00030                             & 0.00037                             & *                                    \\ \hline
Outstar(2)                             & 0.0001                           & 0.00004                             & 0.00015                             & *                                    \\ \hline
Mutual                                 & 0.200                            & 0.123                               & 0.231                               & *                                    \\ \hline
Triangle                               & 0.028                            & 0.027                               & 0.029                               & *                                    \\ \hline
Martin Quinn Score                     & -0.0002                          & -0.0008                             & 0.0006                              &                                      \\ \hline
Same Issue Area Homophily              & 0.0018                           & 0.016                               & 0.019                               & *                                    \\ \hline
Year Difference                        & -0.0007                          & -0.0008                             & -0.0006                             & *                                    \\ \hline
$(\text{Year Differnce})^2$            & 1.326e-07                        & 1.003e-07                           & 1.677e-07                           & *                                    \\ \hline
{\small Receiver Abs Diff MQ Score in Majority} & -0.0003                          & -0.012                              & 0.013                               &                                     \\ \hline
{\small Receiver Number Justices in Majority}   & 0.025                            & 0.006                               & 0.041                               & *                                     \\ \hline
Receiver  Sender Year                  & 0.00001                          & -0.0002                             & 0.0002                              &                                      \\ \hline
Sender Same Issue Area 2               & 0.202                            & 0.101                               & 0.302                               & *                                    \\ \hline
Sender Same Issue Area 3               & -0.304                           & -0.449                              & -0.159                              & *                                    \\ \hline
Sender Same Issue Area 4               & 0.443                            & 0.310                               & 0.586                               & *                                    \\ \hline
Sender Same Issue Area 5               & 0.141                            & -0.104                              & 0.378                               &                                     \\ \hline
Sender Same Issue Area 6               & 0.774                            & 0.568                               & 0.962                               & *                                    \\ \hline
Sender Same Issue Area 7               & 0.604                            & 0.477                               & 0.732                               & *                                    \\ \hline
Sender Same Issue Area 8               & 0.467                            & 0.384                               & 0.564                               & *                                    \\ \hline
Sender Same Issue Area 9               & 0.390                            & 0.292                               & 0.495                               & *                                    \\ \hline
Sender Same Issue Area 10              & 0.450                            & 0.316                               & 0.591                               & *                                    \\ \hline
Sender Same Issue Area 11              & 0.062                            & -0.341                              & 0.376                               &                                      \\ \hline
Sender Same Issue Area 12              & 0.512                            & 0.353                               & 0.674                               & *                                    \\ \hline
Sender Same Issue Area 13              & 0.602                            & 0.238                               & 0.915                               & *                                    \\ \hline
Sender Same Issue Area 14              & 1.442                            & 0.761                               & 1.908                               &  *                                    \\ \hline
Receiver Same Issue Area 2             & 0.171                            & 0.040                               & 0.317                               & *                                    \\ \hline
Receiver Same Issue Area 3             & -0.127                           & -0.310                              & 0.049                               &                                      \\ \hline
Receiver Same Issue Area 4             & 0.326                            & 0.143                               & 0.480                               & *                                    \\ \hline
Receiver Same Issue Area 5             & 0.338                            & 0.037                               & 0.613                               & *                                    \\ \hline
Receiver Same Issue Area 6             & 0.371                            & 0.117                               & 0.596                               & *                                    \\ \hline
Receiver Same Issue Area 7             & 0.305                            & 0.137                               & 0.453                               & *                                    \\ \hline
Receiver Same Issue Area 8             & 0.284                            & 0.166                               & 0.405                               & *                                    \\ \hline
Receiver Same Issue Area 9             & 0.398                            & 0.271                               & 0.523                               & *                                    \\ \hline
Receiver Same Issue Area 10            & 0.419                            & 0.264                               & 0.591                               & *                                    \\ \hline
Receiver Same Issue Area 11            & 0.670                            & 0.395                               & 0.914                               & *                                    \\ \hline
Receiver Same Issue Area 12            & 0.490                            & 0.287                               & 0.687                               & *                                    \\ \hline
Receiver Same Issue Area 13            & 1.045                            & 0.816                               & 1.247                               & *                                    \\ \hline
Receiver Same Issue Area 14            & NA                               & NA                                  & NA                                  &                                      \\ \hline
\end{tabular}
\caption{Bootstrapped MPLE Results for the time period when William Rehnquist was chief justice.}
\label{bootMPLE_rehnquist}
\end{table}
